Automating Verification of MPC Security

### 2023-06-08 popl24/minicat.tex
checkpoint

\begin{example}[One-Time Pad]
  \label{example-otp}
We can model secure communication between two parties
using symmetric key encryption over an insecure channel, for
example. In the following program, we assume $H = \{ 1,2 \}$ and
$C = \{ 0 \}$. Party 1 first shares the randomly generated
key $\fx{1}{0}$ with party 2. Then, party 1 encrypts
its secret $\sx{1}{0}$ and sends it to party 0,
which relays the ciphertext in $\vx{0}{0}$ to
party 2. Finally, party 2 decrypts\footnote{Recall we are using
a random tape approach, so the value of $\fx{1}{0}$ remains
consistent during any run the program, though that value
is randomly determined by the initial memory in a given
run} the ciphertext and stores the plaintext in $\vx{2}{2}$. 
\begin{verbatimtab}
v[2,0] := f[1,0];
v[0,0] := f[1,0] xor s[1,0];
v[2,1] := v[0,0];
v[2,2] := v[2,1] xor v[2,0]
\end{verbatimtab}
This protocol is \emph{correct} because $\vx{2}{2}$ is exactly
correlated with the secret $\sx{1}{0}$, and it is \emph{secure}
because the corrupt view $\vx{0}{0}$ in isolation is probabilistically
independent of the secret $\sx{1}{0}$, while serving as a
communication channel for its encryption. 
\end{example}

>>>>

Here we introduce some examples to illustrate $\minifed$ and how it
can be used to model secure communication protocols for values in the
binary field. Most of these are translations (into $\minifed$) of
object examples in previous related work \cite{XXX}. We will return to
these as running examples throughout the paper to illustrate various
concepts and advantages of our methods.
\begin{example}[One-Time Pad]
  \label{example-otp}
As observed in \cite{XXX} and elsewhere, coin flips with $\exor$ can
be used to model one-time pad encryption in the binary field. On the
basis of this we can model secure communication between over an
insecure channel using symmetric key encryption. In the following
program, we assume $H = \{ 1,2 \}$ and $C = \{ 0 \}$. Client 1 first
shares the randomly generated ``key'' $\fx{1}{0}$ with client 2
through view $\view{2}{0}$. Then, client 1 encrypts its secret
$\sx{1}{0}$ and sends it to party 0, which relays the ciphertext in
$\vx{0}{0}$ to client 2. Finally, client 2 decrypts the the ciphertext
and stores the plaintext in $\vx{2}{2}$.
\begin{verbatimtab}
v[2,0] := f[1,0];
v[0,0] := f[1,0] xor s[1,0];
v[2,1] := v[0,0];
v[2,2] := v[2,1] xor v[2,0]
\end{verbatimtab}
Intuitively, this protocol is \emph{correct} because $\vx{2}{2}$ is
exactly correlated with the secret $\sx{1}{0}$, and it is
\emph{secure} because the corrupt view $\vx{0}{0}$ in isolation is
probabilistically independent of the secret $\sx{1}{0}$.
\end{example}
